---
title: "Gov2k1 Final Paper"
author: "Mohammed Alsobay"
date: "11/24/2021"
output: pdf_document
---

```{r, include=FALSE}
library(tidyverse)
library(ggplot2)
library(here)
library(lme4)
library(stargazer)
library(coefplot)
library(ggstance)
library(broom)
library(data.table)
here::here()

getwd()
```

<!-- Preprocessing -->

```{r, echo=FALSE, warning=FALSE, message=FALSE, results=FALSE}
tweet_cols = c("Tweet1_1", "Tweet1_2", "Tweet1_3",
               "Tweet2_1", "Tweet2_2", "Tweet2_3",
               "Tweet3_1", "Tweet3_2", "Tweet3_3",
               "Tweet4_1", "Tweet4_2", "Tweet4_3",
               "Tweet5_1", "Tweet5_2", "Tweet5_3",
               "Tweet6_1", "Tweet6_2", "Tweet6_3",
               "Tweet7_1", "Tweet7_2", "Tweet7_3",
               "Tweet8_1", "Tweet8_2", "Tweet8_3")

sec_tweets = c(1,2,3,5)
countersec_tweets = c(4,6,7,8)


# %>% select(c(tweet_cols, "Id", "Prmt", "Sect"))
df = read_csv("../data/survey_data.csv")  %>%
  mutate(treatment = as.factor(case_when(Prmt == 1 ~ "Control",
                                         Prmt == 2 ~ "Religious",
                                         Prmt == 3 ~ "National",
                                         Prmt == 4 ~ "ReligiousElite",
                                         Prmt == 5 ~ "NationalElite")),
         Id = as.factor(Id),
         Sect = as.factor(case_when(Sect == 1 ~ "Maronite",
          Sect == 2 ~ "Greek Orthodox",
          Sect == 3 ~ "Catholic",
          Sect == 5 ~ "Armenian Orthodox",
          Sect == 6 ~ "Armenian Catholic",
          Sect == 7 ~ "Sunni",
          Sect == 8 ~ "Shia",
          Sect == 9 ~ "Druze",
          Sect == 10 ~ "Alawite",
          Sect == 11 ~ "Christian min."))) 

df$sect_coarse = as.factor(ifelse(df$Sect %in% c("Sunni", "Shia", "Druze"), yes = as.character(df$Sect), no="Christian"))
df$Sect = relevel(df$Sect, ref="Shia")
df$sect_coarse = relevel(df$sect_coarse, ref="Shia")

isna_cols = paste("isna_", tweet_cols, sep="")

df[,isna_cols] = df %>% select(tweet_cols) %>% is.na() 

df = df %>% mutate(anyna_tweet1 = isna_Tweet1_1 | isna_Tweet1_2 | isna_Tweet1_3,
                   anyna_tweet2 = isna_Tweet2_1 | isna_Tweet2_2 | isna_Tweet2_3,
                   anyna_tweet3 = isna_Tweet3_1 | isna_Tweet3_2 | isna_Tweet3_3,
                   anyna_tweet5 = isna_Tweet5_1 | isna_Tweet5_2 | isna_Tweet5_3,
                   anyna_tweet4 = isna_Tweet4_1 | isna_Tweet4_2 | isna_Tweet4_3,
                   anyna_tweet6 = isna_Tweet6_1 | isna_Tweet6_2 | isna_Tweet6_3,
                   anyna_tweet7 = isna_Tweet7_1 | isna_Tweet7_2 | isna_Tweet7_3,
                   anyna_tweet8 = isna_Tweet8_1 | isna_Tweet8_2 | isna_Tweet8_3,
                   relig_index = df %>% select(matches("relig[0-9]")) %>% rowMeans(),
                   sectarian_index = df %>% select(matches("sectarian[0-9]")) %>% rowMeans(),
                   sectsj_index = df %>% select(matches("sectsj[0-9]")) %>% rowMeans(),
                   mcp_index = df %>% select(matches("mcp[0-9]")) %>% rowMeans())


```


# Todos and Qs:

* Remove stupid grid background in plots 

* Should we try to split the treatment into 2 levels (message and elite) to try and measure the impact of each separately? 
* Druze excluded in religious ID treatment 
* Anchoring vinettes... is this really capturing sectarian sentiment? Seems performative 
* Weirdness in exact matching 
* Druze are excluded in the primes but included in the tweets? 


# Background
In the original paper, the authors conduct two experiments to estimate the effect of counter-sectarian primes on sectarian attitudes: one on Twitter, and another through a field survey. In this section, we respond to the survey experiment, highlighting experimental and analytical decisions that we believe obscure important underlying dynamics of the phenomenon of interest, and the context in which it was studied. 

In the survey experiment, a firm approached a representative sample of 500 participants from Lebanese society and asked them to rate a total of 8 tweets, 4 of which were "sectarian" and 4 of which were "counter-sectarian" in nature. The participants were asked to rate the content of the tweet itself, the person who wrote the tweet, and how likely they were to share the tweet themselves, all on a scale of 1-10, with lower values indiciating negative perception and lower likelihood to share. Participants were randomly assigned to either a control condition, or to receiving one of four priming statements before rating the tweets (translated from Arabic by the authors):

* __Control statement:__ Over the past few years, there has been arise in sectarian tensions in Lebanon and across the Middle East. 
* __National identity prime:__ Over the past few years, there has been arise in sectarian tensions in Lebanon and across the Middle East. _But many people agree that their sect does not make them better than anyone else. They agree that we are all Lebanese and we all should be equal. We all live on one land. We share the same history and the same future; we share the same culture, the same food, and language. Most importantly, we share a common Lebanese identity._
* __Religious identity prime:__ Over the past few years, there has been arise in sectarian tensions in Lebanon and across the Middle East. _But many people agree that their sect does not make them better than anyone else. They agree that we all believe in one God and we should all be equal. We all live on one land, we share the same history and the same future; we share the same culture, the same food, and language. Most importantly, we share a common belief in God._ 
* __Elite-endorsed national ID prime:__ " Over the past few years, there has been a rise in sectarian tensions in Lebanon and across the Middle East. _But many prominent politicians including members of the March 8 bloc, the March 14 bloc, and independents have called for people to come together. They agree that we are all Lebanese..._
* __Elite-endorsed religious ID prime:__ " Over the past few years, there has been a rise in sectarian tensions in Lebanon and across the Middle East. _But many prominent Christian, Sunni, and Shia religious leaders have issued religious decrees calling for people to come together and stop inciting sectarian hatreds. They agree that we all believe in one God..._

The original paper measures the treatment effects on three outcomes of interest: (1) the average rating across all sectarian tweets; (2) the average rating across all counter-sectarian tweets; and (3) total counter-sectarian sentiment, which they define as the difference between (2) and (1). In this response, we argue that the way the outcomes were aggregated in the original paper obscures important heterogeneity in sentiment and response patterns, and introduces complications in understanding the external validity of the study's results. Furthermore, we discuss elements of the experimental design that cast doubt on how well the collected data represents the intended quantity of interest. 

# What is the actual/collected QoI here? 
In this survey experiment, people are visited in-person by an employee of the agency conducting the survey, and are asked to rate the aforementioned tweets on an iPad. Presumably, they are conscious of the fact that they are being observed by the surveyor -- the fact that there is a considerable number of cases where participants refuse to respond to some tweets is evidence of this social pressure. In spirit, the research intends to measure sectarian attitudes and uses ratings provided in the survey as a proxy of such. In practice, what's being measured is _professed attitude to an observer_, which is subtly but importantly different. 

The implication is that the estimated treatment effect of the primes is actually how _what a respondent tells you_ will change, but not necessarily _what they actually feel_, and there's limited reason to expect the two quantities to align, especially when it comes to contentious sectarian content. Under this design, responses may be performative, with subjects answering the way they _think_ the surveyor wants them to, or in a way deemed "socially acceptable". Given this tendency, it's difficult to understand the practical value of these interventions; techniques such as the use of "anchoring vignettes" can help minimize the gap between the two concepts by abstracting the situation away from the self. 

Another peculiarity is that the ratings of the tweets and users closely mirror each other. Across all tweets, ~75% of the ratings match, and ~90% have a difference $\leq 1$. This raises the question of whether tweet and user favorability truly are actually two different but tightly coupled concepts, or whether there may have been something in the phrasing of the survey that lead to this collapse of the two concepts into one. 


```{r, include=FALSE}
#Do people even give different answers for tweet and tweet rating? Seems weird 

for(i in 1:8){
df_temp = df %>% select(matches(paste("^Tweet",i,"_[1-2]", sep=""))) %>% drop_na() 
print(mean(df_temp[,1] == df_temp[,2]))
}


for(i in 1:8){
df_temp = df %>% select(matches(paste("^Tweet",i,"_[1-2]", sep=""))) %>% drop_na() 
print(mean(abs(df_temp[,1] - df_temp[,2]) <= 1))
}
```


# What is actually estimated here?
As confirmed in communication with the authors, survey subjects occasionally refused to answer some of the evaluations, and these were recorded in the data as null values. Out of 500 participants, 28% refused to answer at least one query about a sectarian tweet, and 20% refused to answer at least one query about a counter-sectarian tweet, with 12% of participants refusing to answer at least one query in both categories. Consequently, when the original paper aggregates across tweets by taking an average, any participant that refused to evaluate any of the relevant tweets would have a null value for their aggregated measure. This not only dramatically shrinks the sample size, but also invalidates the work that the expensive surveying firm was hired to do: the sample is no longer representative of Lebanon as a whole, but of those that agreed to evaluate each and every tweet, which is a sub-sample that may differ considerably and is difficult to understand. Because of this, it is difficult to interpret the estimated treatment effects as an average treatment effect for a random Lebanese citizen. 

<!-- Out of 500 participants, 143 refused to evaluate at least one sectarian tweet, 91 refused to evaluate at least one counter-sectarian tweet, and a total of 177 fell in either group. -->



```{r, include=FALSE}
df$isna_sec_tweet_eval = df %>% select(matches("isna_Tweet[1235]_1")) %>% rowSums() > 0

bind_rows(table(df$Sect) / length(df$Sect),
table((df %>% filter(isna_sec_tweet_eval))$Sect) / length((df %>% filter(isna_sec_tweet_eval))$Sect),
table((df %>% filter(!isna_sec_tweet_eval))$Sect) / length((df %>% filter(!isna_sec_tweet_eval))$Sect))



table((df %>% filter(isna_sec_tweet_eval))$Sect) / table(df$Sect)

sum(df %>% select(matches("isna_Tweet[1235]_[1-3]")))
sum(df %>% select(matches("isna_Tweet[4678]_[1-3]")))

df$isna_sec = df %>% select(matches("isna_Tweet[1235]_[1-3]")) %>% rowSums() > 0
df$isna_countersec = df %>% select(matches("isna_Tweet[4678]_[1-3]")) %>% rowSums() > 0
mean(df$isna_sec)
mean(df$isna_countersec)

mean(df$isna_countersec & df$isna_sec)
```

# Disaggregation exposes a more complex sectarian-political dynamic 
The paper reports that the each of the sectarian tweets targets a single sect, with the targeted sects being Sunnis, Shia, Christians, and Druze. On the other hand, the counter-sectarian tweets are generically counter-sectarian, i.e. they call for unity, but do not promote a specific sect. Because people from different sects may respond differently to sectarian tweets and counter-sectarian primes depending on the relationship between their personal sect and the targeted sect, it would be reasonable to expect different treatment efficacy for each of the sectarian tweets, which we explore in this section. 

To contextualize the differences observed between individual tweets in the survey experiment, we contacted the authors for the exact phrasing of the tweets used in Arabic. As native Arabic speakers, we are able to faithfully translate these into English below, and discuss how the nuance of the phrasing affects this experiment: 

__Sectarian tweets:__ 

1. Now the Arab people (or most of them) are certain that _Hezb Al-lat_ is a barbaric, destructive arm of Iran in the region and that it supports its _rawafid_ followers #HezbAllah_is_Lebanons_Destruction 

2. I am a muslim [translator note: female] and I hate non-believers because they do not worship God [Allah]. 

3. To the Christians of the March 8 bloc, how can you allow your future generations to live like you, as followers of an armed party that assassinated the best men of Lebanon? #Lebanon needs a new generation 

4. #Shia muslims spend the night praying to God [Allah] on _Laylat Ul-Qadr_ [translator note: one of the holiest nights of the year in Islam], while _Da'esh_ [ISIS] scum blow up a masjid they are praying in. _Hasbuna Allah Wa Neam Alwakeel_ [translator note: sect-neutral religious saying along the lines of "We leave this to God, and he is the best agent."] #Kabul 

__Counter-sectarian tweets:__ 

1. Did you know that, in Lebanon, we are all Shia if a Shia is threatened, we are all Sunni if a Sunni is threatened, and we are all Christians if a Christian is threatened? #WeAreAllLebanon 

2. There is no hope for Lebanon as long as politicians keep speaking in sectarian logic: Sunni, Shia, Druze, Christian, but nobody says "I am Lebanese". Sectarianism is cancer. 

3. To the devoted sons of the Sunni sect, to the devoted sons of the Shia sect, we do not blame you for a lowly, divisive minority that does not represent you #NoToSectarianism 

4. Lebanon has no economy, no justice system, no oversight, no electoral law, no establishments, no leadership, no authority... etc. Sectarianism infiltrates all of these headlines. #NoToSectarianism 

First, we note that contrary to the paper's claim, none of the counter-sectarian tweets refer to Druze specifically. Second, it's important to note that, with the exception of #2, each of these sectarian tweets is confounded by considerable geopolitical undertones: #1 refers to Iran, #3 is more readily interpreted as an attack on either of the "Free Patriotic Movement" or "Marada" parties, and #4 mixes in the complexities of ISIS perception. In a country where party and religious lines nearly coincide, it is difficult to disentangle political and sectarian sentiment. 

Sectarian tweet #2 highlights a flaw in the experimental design; although it promotes a form of hate, that hate is more accurately described as "anti-atheist" rather than sectarian, as it describes hatred for those who do not believe in or worship God. All the primes emphasize shared identity, with the religious primes specifically highlighting a shared belief in God among religions, and this is likely why we observe in Figure 1 that the primes actually _increase_ support for this tweet (with the exception of the religious elite prime, which has no effect). This example alone highlights the heterogeneity in item-level response and potential unintended harms, which is enough to warrant the disaggregation of the analysis. Furthermore, by disaggregating, we can argue against the following claim in the paper: "the common-national-identity treatment (without elite support) actually had a backlash effect on sectarian tweet ratings, increasing favorability ratings of both the tweets themselves and the users who sent them". We see that, in fact, the national ID prime had null effects on all sectarian tweets except tweet #2, which we've demonstrated is categorically different from the rest; the purported "backlash effect" is not supported by the data. 

Interestingly, when comparing Figure 1 to Figure 2, we see that treatment effects are more stable in the counter-sectarian case. This is in line with our earlier prediction that treatment effects would differ for the sectarian tweets depending on the sect; when the tweets do not promote/hate any specific sect, they should be less distinguishable from each other.




```{r, out.width=1000, echo=FALSE}
#Sectarian disaggregation 

lm_summaries = data.frame()

for (tweet_number in c(1,2,3,5)) {
  for (outcome_number in c(1,2,3)) {
    lm_temp = lm(paste("Tweet",tweet_number,"_",outcome_number,"~treatment", sep=""), data=df)
    lm_summaries = bind_rows(lm_summaries, 
                             tidy(lm_temp) %>% 
                               mutate(tweet_number = tweet_number,
                                      outcome_number = outcome_number))
  }
}

lm_summaries = lm_summaries %>% mutate(tweet_number = as.factor(tweet_number), outcome_number = as.factor(outcome_number))
lm_summaries$outcome_label = factor(case_when(lm_summaries$outcome_number == 1 ~ "Tweet Rating",
                                       lm_summaries$outcome_number == 2 ~ "User Rating",
                                       lm_summaries$outcome_number == 3 ~ "Likelihood to Share"))

lm_summaries$term = str_remove(lm_summaries$term, "treatment")
lm_summaries$tweet_number_clean = factor(case_when(lm_summaries$tweet_number == 1 ~ "Sectarian #1",
                                                   lm_summaries$tweet_number == 2 ~ "Sectarian #2",
                                                   lm_summaries$tweet_number == 3 ~ "Sectarian #3",
                                                   lm_summaries$tweet_number == 5 ~ "Sectarian #4"))


#Summarizing plot 
lm_summaries %>% filter(term != "(Intercept)") %>%  
  ggplot(aes(x=estimate, y=term, xmin=estimate-1.96*std.error, xmax=estimate+1.96*std.error, color=tweet_number_clean)) + 
  labs(title="Fig 1. Effect of treatments on sectarian tweet evaluations") + 
  geom_point(position=ggstance::position_dodgev(height=0.5)) +
  geom_errorbar(position=ggstance::position_dodgev(height=0.5)) + 
  geom_vline(xintercept=0) + 
  facet_grid(.~factor(outcome_label, levels=c("Tweet Rating", "User Rating", "Likelihood to Share"))) + 
  labs(y="Treatment", x="Estimate", color="Tweet Number")
```


```{r, out.width=1000, echo=FALSE}
#Counter-sectarian disaggregation 

lm_summaries = data.frame()

for (tweet_number in c(4,6,7,8)) {
  for (outcome_number in c(1,2,3)) {
    lm_temp = lm(paste("Tweet",tweet_number,"_",outcome_number,"~treatment", sep=""), data=df)
    lm_summaries = bind_rows(lm_summaries, 
                             tidy(lm_temp) %>% 
                               mutate(tweet_number = tweet_number,
                                      outcome_number = outcome_number))
  }
}

lm_summaries = lm_summaries %>% mutate(tweet_number = as.factor(tweet_number), outcome_number = as.factor(outcome_number))
lm_summaries$outcome_label = factor(case_when(lm_summaries$outcome_number == 1 ~ "Tweet Rating",
                                       lm_summaries$outcome_number == 2 ~ "User Rating",
                                       lm_summaries$outcome_number == 3 ~ "Likelihood to Share"))

lm_summaries$term = str_remove(lm_summaries$term, "treatment")
lm_summaries$tweet_number_clean = factor(case_when(lm_summaries$tweet_number == 4 ~ "Counter-sectarian #1",
                                                   lm_summaries$tweet_number == 6 ~ "Counter-sectarian #2",
                                                   lm_summaries$tweet_number == 7 ~ "Counter-sectarian #3",
                                                   lm_summaries$tweet_number == 8 ~ "Counter-sectarian #4"))

#Summarizing plot 
lm_summaries %>% filter(term != "(Intercept)") %>%  
  ggplot(aes(x=estimate, y=term, xmin=estimate-1.96*std.error, xmax=estimate+1.96*std.error, color=tweet_number_clean)) + 
  labs(title="Fig 2. Effect of treatments on sectarian tweet evaluations") + 
  geom_point(position=ggstance::position_dodgev(height=0.5)) +
  geom_errorbar(position=ggstance::position_dodgev(height=0.5)) + 
  geom_vline(xintercept=0) + 
  facet_grid(.~factor(outcome_label, levels=c("Tweet Rating", "User Rating", "Likelihood to Share"))) + 
  labs(y="Treatment", x="Estimate", color="Tweet Number")
```



<!-- # Interactions and inclusion/exclusion of Druze -->
<!-- To be completed.  -->


# Exploring patterns of non-response 
The original paper reports that "...one of the strongest predictors of unfavorable ratings for sectarian tweets and favorable ratings for counter-sectarian tweets in our survey experiment was users’ level of motivation to control prejudice (MCP)--their concern with acting prejudiced or being perceived as prejudiced." To measure this, they regress the aggregated composite measure highlighted in the background section of this report on several controls, including MCP. Putting aside our concerns regarding the aggregation, the patterns of non-response present an interesting opportunity to test the validity of the MCP measure. Following the logic outlined by the authors, MCP should be predictive of non-response, as fear of impropriety is supposedly the motive behind refusing to answer. In Tables 1 & 2, we find that MCP is not meaningfully associated with non-response for both sectarian and counter-sectarian tweets. 

On the other hand, and quite intuitively, we find that the respondent's sect has a large and significant effect on non-response for sectarian tweets (with the exception of #2, which we have previously demonstrated is categorically different). We find no reliable predictors of non-response for counter-sectarian tweets, making a puzzling behavior even more puzzling.  



```{r, results='asis', echo=FALSE}
stargazer(lm(anyna_tweet1 ~ sect_coarse + polinterest + socmedia + relig_index + sectarian_index + sectsj_index + mcp_index, data=df),
          lm(anyna_tweet2 ~ sect_coarse + polinterest + socmedia + relig_index + sectarian_index + sectsj_index + mcp_index, data=df),
          lm(anyna_tweet3 ~ sect_coarse + polinterest + socmedia + relig_index + sectarian_index + sectsj_index + mcp_index, data=df),
          lm(anyna_tweet5 ~ sect_coarse + polinterest + socmedia + relig_index + sectarian_index + sectsj_index + mcp_index, data=df), 
          type="latex", title="Estimating effects on non-response for sectarian tweets", header=FALSE,
          dep.var.labels = c("NA Tweet 1", "NA Tweet 2", "NA Tweet 3", "NA Tweet 4"))

stargazer(lm(anyna_tweet4 ~ sect_coarse + polinterest + socmedia + relig_index + sectarian_index + sectsj_index + mcp_index, data=df),
          lm(anyna_tweet6 ~ sect_coarse + polinterest + socmedia + relig_index + sectarian_index + sectsj_index + mcp_index, data=df),
          lm(anyna_tweet7 ~ sect_coarse + polinterest + socmedia + relig_index + sectarian_index + sectsj_index + mcp_index, data=df),
          lm(anyna_tweet8 ~ sect_coarse + polinterest + socmedia + relig_index + sectarian_index + sectsj_index + mcp_index, data=df), 
          type="latex", title="Estimating effects on non-response for counter-sectarian tweets", header=FALSE,
          dep.var.labels = c("NA Tweet 1", "NA Tweet 2", "NA Tweet 3", "NA Tweet 4"))
```




<!-- ```{r, include=FALSE} -->
<!-- #Look at blocks of behavior  -->
<!-- (df %>% group_by(across(all_of(isna_cols))) %>% count() %>% arrange(desc(n)))[6,] -->

<!-- #Average by columns -->
<!-- df %>% select(tweet_cols) %>% is.na() %>% colMeans() %>% sort(decreasing = TRUE)  -->
<!-- df %>% select(tweet_cols) %>% is.na() %>% colMeans()  -->
<!-- ``` -->











<!-- ## Interactions -->

<!-- ### Sectarian -->

<!-- ```{r, fig.width=15} -->

<!-- lm_summaries = data.frame() -->

<!-- for (tweet_number in c(1,2,3,5)) { -->
<!--   for (outcome_number in c(1,2,3)) { -->
<!--     lm_temp = lm(paste("Tweet",tweet_number,"_",outcome_number,"~treatment*sect_coarse", sep=""), data=df) -->
<!--     lm_summaries = bind_rows(lm_summaries,  -->
<!--                              tidy(lm_temp) %>%  -->
<!--                                mutate(tweet_number = tweet_number, -->
<!--                                       outcome_number = outcome_number)) -->
<!--   } -->
<!-- } -->

<!-- lm_summaries = lm_summaries %>% mutate(tweet_number = as.factor(tweet_number), outcome_number = as.factor(outcome_number)) -->


<!-- # lm_summaries %>% filter(outcome_number == 1 & (lm_summaries$term %like% ":")) %>%   -->
<!-- #   ggplot(aes(x=estimate, y=term, xmin=estimate-1.96*std.error, xmax=estimate+1.96*std.error, color=tweet_number)) +  -->
<!-- #   geom_point(position=ggstance::position_dodgev(height=0.5)) + -->
<!-- #   labs(title="Tweet Rating") + -->
<!-- #   geom_errorbar(position=ggstance::position_dodgev(height=0.5)) +  -->
<!-- #   geom_vline(xintercept=0) -->


<!-- lm_summaries %>% filter((lm_summaries$term %like% "treatment")) %>%   -->
<!--   ggplot(aes(x=estimate, y=term, xmin=estimate-1.96*std.error, xmax=estimate+1.96*std.error, color=tweet_number)) +  -->
<!--   labs(title="Sectarian tweets") +  -->
<!--   geom_point(position=ggstance::position_dodgev(height=0.5)) + -->
<!--   geom_errorbar(position=ggstance::position_dodgev(height=0.5)) +  -->
<!--   geom_vline(xintercept=0) +  -->
<!--   facet_grid(.~outcome_number) -->


<!-- lm_summaries %>% filter(p.value <= 0.05 & term != "(Intercept)") -->

<!-- ``` -->

<!-- ### Countersec  -->

<!-- ```{r, fig.width=15} -->

<!-- lm_summaries = data.frame() -->

<!-- for (tweet_number in c(4, 6,7,8)) { -->
<!--   for (outcome_number in c(1,2,3)) { -->
<!--     lm_temp = lm(paste("Tweet",tweet_number,"_",outcome_number,"~treatment*sect_coarse", sep=""), data=df) -->
<!--     lm_summaries = bind_rows(lm_summaries,  -->
<!--                              tidy(lm_temp) %>%  -->
<!--                                mutate(tweet_number = tweet_number, -->
<!--                                       outcome_number = outcome_number)) -->
<!--   } -->
<!-- } -->

<!-- lm_summaries = lm_summaries %>% mutate(tweet_number = as.factor(tweet_number), outcome_number = as.factor(outcome_number)) -->


<!-- # lm_summaries %>% filter(outcome_number == 1 & (lm_summaries$term %like% ":")) %>%   -->
<!-- #   ggplot(aes(x=estimate, y=term, xmin=estimate-1.96*std.error, xmax=estimate+1.96*std.error, color=tweet_number)) +  -->
<!-- #   geom_point(position=ggstance::position_dodgev(height=0.5)) + -->
<!-- #   labs(title="Tweet Rating") + -->
<!-- #   geom_errorbar(position=ggstance::position_dodgev(height=0.5)) +  -->
<!-- #   geom_vline(xintercept=0) -->


<!-- lm_summaries %>% filter((lm_summaries$term %like% "treatment")) %>%   -->
<!--   ggplot(aes(x=estimate, y=term, xmin=estimate-1.96*std.error, xmax=estimate+1.96*std.error, color=tweet_number)) +  -->
<!--   labs(title="Countersec tweets") +  -->
<!--   geom_point(position=ggstance::position_dodgev(height=0.5)) + -->
<!--   geom_errorbar(position=ggstance::position_dodgev(height=0.5)) +  -->
<!--   geom_vline(xintercept=0) +  -->
<!--   facet_grid(.~outcome_number) -->



<!-- lm_summaries %>% filter(p.value <= 0.05 & term != "(Intercept)") -->

<!-- ``` -->



<!-- # Non-response (NR) patterns  -->

<!-- ## Patterns of NR -->

<!-- * break down into unit and item-level patterns  -->





<!-- # Predicting nonresponse  -->

<!-- ```{r, results='asis'} -->
<!-- df %>% select(matches("any")) %>% colMeans() -->
<!-- #  -->
<!-- #  -->
<!-- # stargazer(lm(anyna_tweet1 ~ sect_coarse + polinterest + socmedia, data=df), -->
<!-- #           lm(anyna_tweet2 ~ sect_coarse + polinterest + socmedia, data=df), -->
<!-- #           lm(anyna_tweet3 ~ sect_coarse + polinterest + socmedia, data=df), -->
<!-- #           lm(anyna_tweet5 ~ sect_coarse + polinterest + socmedia, data=df), type="text") -->


<!-- df %>% select(c("sect_coarse", "polinterest", "socmedia", "relig_index", "sectarian_index", "sectsj_index", "mcp_index")) %>% is.na() %>% colMeans() -->


<!-- stargazer(lm(anyna_tweet1 ~ sect_coarse + polinterest + socmedia + relig_index + sectarian_index + sectsj_index + mcp_index, data=df), -->
<!--           lm(anyna_tweet2 ~ sect_coarse + polinterest + socmedia + relig_index + sectarian_index + sectsj_index + mcp_index, data=df), -->
<!--           lm(anyna_tweet3 ~ sect_coarse + polinterest + socmedia + relig_index + sectarian_index + sectsj_index + mcp_index, data=df), -->
<!--           lm(anyna_tweet5 ~ sect_coarse + polinterest + socmedia + relig_index + sectarian_index + sectsj_index + mcp_index, data=df), -->
<!--           lm(anyna_tweet4 ~ sect_coarse + polinterest + socmedia + relig_index + sectarian_index + sectsj_index + mcp_index, data=df), -->
<!--           lm(anyna_tweet6 ~ sect_coarse + polinterest + socmedia + relig_index + sectarian_index + sectsj_index + mcp_index, data=df), -->
<!--           lm(anyna_tweet7 ~ sect_coarse + polinterest + socmedia + relig_index + sectarian_index + sectsj_index + mcp_index, data=df), -->
<!--           lm(anyna_tweet8 ~ sect_coarse + polinterest + socmedia + relig_index + sectarian_index + sectsj_index + mcp_index, data=df), type="latex") -->




<!-- ``` -->



<!-- # What if analysis on nonresponse?  -->

<!-- ```{r} -->
<!-- summary(lm(Tweet1_1 ~ treatment, data=df)) -->
<!-- summary(lm(Tweet1_1 ~ treatment, data=df %>% replace_na(list("Tweet1_1" = 1)))) -->
<!-- summary(lm(Tweet1_1 ~ treatment, data=df %>% replace_na(list("Tweet1_1" = 10)))) -->


<!-- summary(lm(Tweet2_1 ~ treatment, data=df)) -->
<!-- summary(lm(Tweet2_1 ~ treatment, data=df %>% replace_na(list("Tweet2_1" = 1)))) -->
<!-- summary(lm(Tweet2_1 ~ treatment, data=df %>% replace_na(list("Tweet2_1" = 10)))) -->

<!-- summary(lm(Tweet3_1 ~ treatment, data=df)) -->
<!-- summary(lm(Tweet3_1 ~ treatment, data=df %>% replace_na(list("Tweet3_1" = 1)))) -->
<!-- summary(lm(Tweet3_1 ~ treatment, data=df %>% replace_na(list("Tweet3_1" = 10)))) -->

<!-- summary(lm(Tweet5_1 ~ treatment, data=df)) -->
<!-- summary(lm(Tweet5_1 ~ treatment, data=df %>% replace_na(list("Tweet5_1" = 1)))) -->
<!-- summary(lm(Tweet5_1 ~ treatment, data=df %>% replace_na(list("Tweet5_1" = 10)))) -->

<!-- ``` -->





