---
title: "Replication_1129_Sumaya's Part"
author: "Mohammed Alsobay, Sumaya Malas, Tianyu Qiao (Team 2.5 Arabs)"
date: "11/29/2021"
output: pdf_document
urlcolor: blue
---


```{r, message = FALSE, warning = FALSE, echo=FALSE}
#Twitter script packages 
library(readr)
library(ggplot2)
library(coefplot)
library(dplyr)
library(psych)
library(MASS)
library(xtable)
library(stargazer)
library(knitr)
```

```{r, include=FALSE}
here::here()
```


# Clustered Standard Errors for Survey Experiment
Clustered standard errors: The survey data included information on the subject’s geography, which was not used in either of the basic OLS estimates reported in the paper, or the controlled regressions in the appendix. Given the context of Lebanon’s consociational democracy and ethnic distribution based on religious sect, we want to cluster the standard errors of the treatment effect by the different geographic/administrative levels provided to assess the robustness of the findings.

```{r, echo=FALSE, message=FALSE}
# Survey data preprocessing 
rm(list = ls())


#Read in Data
data<-read_csv("../data/survey_data.csv")

#Prepare Data for Analysis 

#Covariate Indices (average responses)
data$relig<-(data$relig1+data$relig2+data$relig3+data$relig4+data$relig5+data$relig6+data$relig7+data$relig8+data$relig9+data$relig10+data$relig11+data$relig12)/12
data$sectarian<-(data$sectarian1+data$sectarian2+data$sectarian3+data$sectarian4+data$sectarian5)/5
data$sectsj<-(data$sectsj1+data$sectsj2+data$sectsj3+data$sectsj4+data$sectsj5+data$sectsj6+data$sectsj7+data$sectsj8)/8
data$mcp<-(data$mcp1+data$mcp2+data$mcp3+data$mcp4+data$mcp5+data$mcp6+data$mcp7+data$mcp8+data$mcp9+data$mcp10+data$mcp11)/11

#Sect Variables
data$maronite<-ifelse(data$Sect==1, 1,0)
data$sunni<-ifelse(data$Sect==7, 1,0)
data$shia<-ifelse(data$Sect==8, 1,0)

#Counter Sectarian Tweets
#rating
data$counter_sec1<-(data$Tweet8_1+data$Tweet6_1+data$Tweet4_1+data$Tweet7_1)/4
#person rating
data$counter_sec2<-(data$Tweet8_2+data$Tweet6_2+data$Tweet4_2+data$Tweet7_2)/4
#sharing likelihood
data$counter_sec3<-(data$Tweet8_3+data$Tweet6_3+data$Tweet4_3+data$Tweet7_3)/4
# hist(data$counter_sec3)

#Sectarian Tweets 
#rating
data$sec1<-(data$Tweet1_1+data$Tweet2_1+data$Tweet3_1+data$Tweet5_1)/4
#person rating
data$sec2<-(data$Tweet1_2+data$Tweet2_2+data$Tweet3_2+data$Tweet5_2)/4
#sharing likelihood
data$sec3<-(data$Tweet1_3+data$Tweet2_3+data$Tweet3_3+data$Tweet5_3)/4

#Counter Sectarian Ratings - Sectarian Ratings
data$combined1<-data$sec1-data$counter_sec1
data$combined2<-data$sec2-data$counter_sec2
data$combined3<-data$sec3-data$counter_sec3

#Treatment Var
data$treatment<-as.factor(data$Prmt)


```


```{r, out.width="400px", out.height="300px", message=FALSE}
library(lmtest)
library(sandwich)
library(ggplot2)
library(broom)
library(RobustSE)
#install.packages("pacman")
library(pacman)
library(data.table)
library(magrittr)
#install.packages("fixest")
library(fixest)

#Regressions for model 1- tweet rating in Figure 6
model1<-feols(combined1~treatment, data=data)

mod1_Mohafaza<- feols(combined1~ treatment+Mohafaza, data= data)

mod1_Caza<- feols(combined1~ treatment+ Caza, data= data) 

mod1_City<- feols(combined1~ treatment+ City, data= data)

#Standard Errors
etable(model1, mod1_Mohafaza, mod1_Caza, mod1_City, se= "standard")

etable(model1, mod1_Mohafaza, mod1_Caza, mod1_City, se= "hetero")

etable(model1, mod1_Mohafaza, mod1_Caza, mod1_City, se= "cluster", cluster = c( "City"))


#Regressions for model 2- User rating in Figure 6
model2<-feols(combined2~treatment, data=data)

mod2_Mohafaza<- feols(combined2~ treatment+Mohafaza, data= data)

mod2_Caza<- feols(combined2~ treatment+ Caza, data= data) 

mod2_City<- feols(combined2~ treatment+ City, data= data)

#Standard Errors
etable(model2, mod2_Mohafaza, mod2_Caza, mod2_City, se= "standard")

etable(model2, mod2_Mohafaza, mod2_Caza, mod2_City, se= "hetero")

etable(model2, mod2_Mohafaza, mod2_Caza, mod2_City, se= "cluster", cluster = c( "City"))



#Regressions for model 3- Likely to share in Figure 6
model3<-feols(combined3~treatment, data=data)

mod3_Mohafaza<- feols(combined3~ treatment+Mohafaza, data= data)

mod3_Caza<- feols(combined3~ treatment+ Caza, data= data) 

mod3_City<- feols(combined3~ treatment+ City, data= data)

#Standard Errors
etable(model3, mod3_Mohafaza, mod3_Caza, mod3_City, se= "standard")

etable(model3, mod3_Mohafaza, mod3_Caza, mod3_City, se= "hetero")

etable(model3, mod3_Mohafaza, mod3_Caza, mod3_City, se= "cluster", cluster = c( "City"))


```

\newpage
# Figure 7: Effect of Primes on (a) Sectarian and (b) Counter-Sectarian Tweet Ratings

## Figure 7a: 


```{r, out.width="400px", out.height="300px", message=FALSE}
#Regressions for model 1- tweet rating in Figure 7a
model1<-feols(sec1~treatment, data=data)

mod1_Mohafaza<- feols(sec1~treatment+ Mohafaza, data= data)

mod1_Caza<- feols(sec1~treatment+ Caza, data= data) 

mod1_City<- feols(sec1~treatment+ City, data= data)

#Standard Errors
etable(model1, mod1_Mohafaza, mod1_Caza, mod1_City, se= "standard")

etable(model1, mod1_Mohafaza, mod1_Caza, mod1_City, se= "hetero")

etable(model1, mod1_Mohafaza, mod1_Caza, mod1_City, se= "cluster", cluster = c( "City"))



#Regressions for model 2- User rating in Figure 7a
model2<-feols(sec2~treatment, data=data)

mod2_Mohafaza<- feols(sec2~treatment+Mohafaza, data= data)

mod2_Caza<- feols(sec2~treatment+ Caza, data= data) 

mod2_City<- feols(sec2~treatment+ City, data= data)

#Standard Errors
etable(model2, mod2_Mohafaza, mod2_Caza, mod2_City, se= "standard")

etable(model2, mod2_Mohafaza, mod2_Caza, mod2_City, se= "hetero")

etable(model2, mod2_Mohafaza, mod2_Caza, mod2_City, se= "cluster", cluster = c( "City"))



#Regressions for model 3- Likely to share in Figure 7a
model3<-feols(sec3~treatment, data=data)

mod3_Mohafaza<- feols(sec3~treatment+Mohafaza, data= data)

mod3_Caza<- feols(sec3~treatment+ Caza, data= data) 

mod3_City<- feols(sec3~treatment+ City, data= data)

#Standard Errors
etable(model3, mod3_Mohafaza, mod3_Caza, mod3_City, se= "standard")

etable(model3, mod3_Mohafaza, mod3_Caza, mod3_City, se= "hetero")

etable(model3, mod3_Mohafaza, mod3_Caza, mod3_City, se= "cluster", cluster = c( "City"))


```



\newpage
### Figure 7b:
 

```{r, out.width="400px", out.height="300px", message=FALSE}
#Regressions for model 1- tweet rating in Figure 7b
model1<-feols(counter_sec1~treatment, data=data)

mod1_Mohafaza<- feols(counter_sec1~treatment+ Mohafaza, data= data)

mod1_Caza<- feols(counter_sec1~treatment+ Caza, data= data) 

mod1_City<- feols(counter_sec1~treatment+ City, data= data)

#Standard Errors
etable(model1, mod1_Mohafaza, mod1_Caza, mod1_City, se= "standard")

etable(model1, mod1_Mohafaza, mod1_Caza, mod1_City, se= "hetero")

etable(model1, mod1_Mohafaza, mod1_Caza, mod1_City, se= "cluster", cluster = c( "City"))



#Regressions for model 2- User rating in Figure 7b
model2<-feols(counter_sec2~treatment, data=data)

mod2_Mohafaza<- feols(counter_sec2~treatment+Mohafaza, data= data)

mod2_Caza<- feols(counter_sec2~treatment+ Caza, data= data) 

mod2_City<- feols(counter_sec2~treatment+ City, data= data)

#Standard Errors
etable(model2, mod2_Mohafaza, mod2_Caza, mod2_City, se= "standard")

etable(model2, mod2_Mohafaza, mod2_Caza, mod2_City, se= "hetero")

etable(model2, mod2_Mohafaza, mod2_Caza, mod2_City, se= "cluster", cluster = c( "City"))



#Regressions for model 3- Likely to share in Figure 7b
model3<-feols(counter_sec3~treatment, data=data)

mod3_Mohafaza<- feols(counter_sec3~treatment+Mohafaza, data= data)

mod3_Caza<- feols(counter_sec3~treatment+ Caza, data= data) 

mod3_City<- feols(counter_sec3~treatment+ City, data= data)

#Standard Errors
etable(model3, mod3_Mohafaza, mod3_Caza, mod3_City, se= "standard")

etable(model3, mod3_Mohafaza, mod3_Caza, mod3_City, se= "hetero")

etable(model3, mod3_Mohafaza, mod3_Caza, mod3_City, se= "cluster", cluster = c( "City"))



```
